### 2018-02-05 Cars/paper.tex
convert feet to metres in code (not paper)

@@

\section{Conclusion}
\begin{itemize}
\item Fitting individual AR 2 models on each driver's velocity and steering angle drastically improves forecasts of the future trajectory compared to the constant model used in practice
\item Strong prior information improves forecasts early on in the sample, but has a reduced impact after ~20 seconds of observation
\item Constantly fitting individual models in this way can be made computationally feasible by updating previous Variational Bayes model fits, which incurs only a small performance hit relative to the more expensive standard VB and MCMC methods.
\end{itemize}

>>>>

\begin{center}
\begin{table}[h]
\begin{tabular}{| l | c | c | c |}
\hline
& Non-Informative Prior & Simple Hierarchy & Finite Mixture Hierarchy \\
\hline
MCMC & 0.81 & 0.77 & 0.77 \\
VB Standard & 0.79 & 0.77 & 0.77 \\
VB Updating & 0.79 & 0.78 & 0.77 \\
\hline
\end{tabular}
\label{tableError}
\caption{Mean predictive Euclidean error in feet for $p(z_{i, T+h} | z_{i, 1:T})$ for $h = 1, \dots, 30$ and $T = \{10, 20, \dots, 300\}$ for each prior and algorithm combination. The mean predictive Euclidean error for the constant velocity / angle model is 3.26 feet.}
\end{table}
\end{center}

@@

\section{Conclusion}
\begin{itemize}
\item Fitting individual AR 2 models on each driver's velocity and steering angle drastically improves forecasts of the future trajectory compared to the constant model used in practice
\item Strong prior information improves forecasts early on in the sample, but has a reduced impact after ~20 seconds of observation.
\item Constantly fitting individual models in this way can be made computationally feasible by updating previous Variational Bayes model fits, which incurs only a small performance hit relative to the more expensive standard VB and MCMC methods.
\end{itemize}
